### 2024-06-02 2024-5-13/sections/implementation.tex
fix the syntax error in implementation

We implemented the procedures and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
%
In this section, we evaluate the performance of $\ostrichrecl$ on three benchmark suites, that is, RegCoL, AutomatArk, and NestC. In the sequel, we first describe the three benchmark suites as well as the experiment setup. Then we present the experiment results. We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}. We also compare $\ostrichrecl$ with several variants of itself, to evaluate the effectiveness of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}.

% We do experiments to compare the performance of $\ostrichrecl$ with the state-of-the-art string solvers. Moreover, in order to know whether $\ostrichrecl$ is good at solving string constraints with large counting and length, we extract \denghang{todo} instances with large bounds out of , and compare the performance of $\ostrichrecl$ with the other solvers on these instances. Finally, we empirically justify the technical choices made in the decision procedure of Section~\ref{subsec:cefadec} by comparing $\ostrichrecl$ with the following two variants of $\ostrichrecl$: $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$, where $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$ are obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 in Section~\ref{subsec:cefadec}) and using the nuXmv model checker to solve the nonemptiness of $\cefadec$ respectively.

@@

\medskip
\noindent
\emph{Distribution of problem instances w.r.t. counting bounds. }
The distribution of problem instances w.r.t. the counting bounds in the three suites is shown in Fig~\ref{fig:count_distri}, where the $x$-axis represents the counting bound and the $y$-axis represents the number of problem instances containing the counting bound. 
%The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
In our statistics, while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e. greater than or equal to $50$).
%Although most upper bounds are small, about two thousand of them are still greater than 50.

@@

At first, we do experiments to evaluate the effectiveness of the automata size-reduction techniques (i.e. Step 2) in Section~\ref{sec:algorithm}. Then we justify our technical choices of reducing the satisfiability problem to that of LIA formulas and resort to the SMT solvers to solve them. Specifically, we compare $\ostrichrecl$ with a variant where the nuXmv model checker like \cite{atva2020} is used to solve the $\cefadec$ problem. 
%
%We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. 
We also evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}, i.e. the optimizations for the nesting of counting operators as well as the nesting of counting operators and a complement operator. Finally, we evaluate the effectiveness of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}.

@@

%Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results. Therefore, we consider the NestC benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes. The NestC benchmark experiment results is shown in Table~\ref{tab:results_heuristic_complex}. We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively. From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the non-register-representable regexes.

@@

The experiment results can be found in Table~\ref{tab:results_model-gen}. From the results, we can see that compared to $\ostrichrecl$, $\ostrichrecl_{\rm -MODEL}$ solves 349 less instances and is 23\% slower on average (3.57s versus 2.88s). As a result, the optimization for the model generation does improve the performance, especially when the sizes of the CEFAs are huge.  
Note that the optimization for model generation only affects the satisfiable instances, that is, those instances where the generated LIA formulas can be solved, but the generation of models for these RECL constraints is unsuccessful.

>>>>

We implemented the procedures and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen} on top of OSTRICH, resulting in a string solver called $\ostrichrecl$. 
%
In this section, we evaluate the performance of $\ostrichrecl$ on three benchmark suites, that is, RegCoL, AutomatArk, and NestC. In the sequel, we first describe the three benchmark suites as well as the experiment setup. Then we present the experiment results. We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}. We also compare $\ostrichrecl$ with several variants of itself, to evaluate the effectiveness of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}.

% We do experiments to compare the performance of $\ostrichrecl$ with the state-of-the-art string solvers. Moreover, in order to know whether $\ostrichrecl$ is good at solving string constraints with large counting and length, we extract \denghang{todo} instances with large bounds out of, and compare the performance of $\ostrichrecl$ with the other solvers on these instances. Finally, we empirically justify the technical choices made in the decision procedure of Section~\ref{subsec:cefadec} by comparing $\ostrichrecl$ with the following two variants of $\ostrichrecl$: $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$, where $\ostrichrecl_{\rm - ASR}$ and $\ostrichrecl_{\rm NUXMV}$ are obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 in Section~\ref{subsec:cefadec}) and using the nuXmv model checker to solve the nonemptiness of $\cefadec$ respectively.

@@

\medskip
\noindent
\emph{Distribution of problem instances w.r.t. counting bounds. }
The distribution of problem instances w.r.t. the counting bounds in the three suites is shown in Fig~\ref{fig:count_distri}, where the $x$-axis represents the counting bound and the $y$-axis represents the number of problem instances containing the counting bound. 
%The upper bound is the number $n$ of regex $e^{\{m,n\}}, e^{\{n,n\}}$ and $e^{\{n,\infty\}}$ (which is equivalent to $e^{\{n,n\}}e^*$). 
In our statistics, while most problem instances contain only small bounds, there are still around 3,000  (about 6\%) of them using large counting bounds (i.e., greater than or equal to $50$).
%Although most upper bounds are small, about two thousand of them are still greater than 50.

@@

At first, we do experiments to evaluate the effectiveness of the automata size-reduction techniques (i.e., Step 2) in Section~\ref{sec:algorithm}. Then we justify our technical choices of reducing the satisfiability problem to that of LIA formulas and resort to the SMT solvers to solve them. Specifically, we compare $\ostrichrecl$ with a variant where the nuXmv model checker like \cite{atva2020} is used to solve the $\cefadec$ problem. 
%
%We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. 
We also evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}, i.e., the optimizations for the nesting of counting operators as well as the nesting of counting operators and a complement operator. Finally, we evaluate the effectiveness of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}.

@@

%Since the non-register-representable regexes collected from real world are few (5\% of RegCoL and AutomatArk benchmark suites) and simple, there seems no much difference between the performance of $\ostrichrecl$ and its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$ in the overall experiment results. Therefore, we consider the NestC benchmark suite, which contains more complex non-register-representable regexes, to justify the optimizations for non-register-representable regexes. The NestC benchmark experiment results are shown in Table~\ref{tab:results_heuristic_complex}. We can see that $\ostrichrecl$ solves 82/339/326 more instances and is 1.02/1.92/1.61 times faster than ${\rm -NEST}$/${\rm -COMP}$/${\rm -FIND}$ respectively. From the results, we can conclude that all the optimizations sharply improve the performance of $\ostrichrecl$ on the non-register-representable regexes.

@@

The experiment results can be found in Table~\ref{tab:results_model-gen}. From the results, we can see that compared to $\ostrichrecl$, $\ostrichrecl_{\rm -MODEL}$ solves 349 fewer instances and is 23\% slower on average (3.57s versus 2.88s). As a result, the optimization for the model generation does improve the performance, especially when the sizes of the CEFAs are huge.  
Note that the optimization for model generation only affects the satisfiable instances, that is, those instances where the generated LIA formulas can be solved, but the generation of models for these RECL constraints is unsuccessful.
